Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-05-23 mu/article/article.tex
ChWS

\section{Introduction}
\blindtext
\begin{figure}[ht!]
    \centering
    \includegraphics[width=\linewidth]{figures/altstruc2}
    \label{fig:alt-struc-xz}
    \\
    \includegraphics[width=\linewidth]{figures/altstruc1}
    \label{fig:alt-struc-xy}
    \caption{Alt structure.}
    \label{fig:alt-struc}
\end{figure}
\begin{figure}[ht!]
    \centering
    \includegraphics[width=\linewidth]{figures/upstruc2}
    \label{fig:up-struc-xz}
    \\
    \includegraphics[width=\linewidth]{figures/upstruc1}
    \label{fig:up-struc-xy}
    \caption{Up structure}
    \label{fig:up-struc}
\end{figure}
\blindtext
\blindtext

@@

The spin density injection current $\dot{K}^{\mathrm{ab}}$ with speed along
direction $\mathrm{a}$ and spin polarization along $\mathrm{b}$ is defined as
\begin{equation}
\dot{K}(\omega) = \mu^{\mathrm{abcd}}(\omega)
E^{\mathrm{c}}(\omega) E^{\mathrm{d*}}(\omega)
\label{eq:dotk}
\end{equation}
where
\begin{widetext}
\begin{align}
\mu^{\mathrm{abcd}} (\omega) 
&=
\frac{\pi e^{2}}{\hbar^{2}} \int 
\frac{d^{3}K}{8 \pi^{3}} \sum_{vcc'}^{'}
\mathrm{Re} \left[ K^{\mathrm{ab}}_{cc'} ( 
r^{\mathrm{c}}_{vc'} 
r^{\mathrm{d}}_{cv } +
r^{\mathrm{d}}_{vc'} 
r^{\mathrm{c}}_{cv } ) \right]
\delta(\omega-\omega_{cv})
\label{eq:mu}
\\
K^{\mathrm{ab}}_{mn}
&=
\sum_{\ell}v^{\mathrm{a}}_{nl} S^{\mathrm{b}}_{lm}
\label{eq:velspi-matelem}
\end{align}
\end{widetext}
is the corresponding spin density injection current pseudotensor. The $'$
in the sum means that $c$ and $c'$ are quasi degenerate states and the sum only
covers these states.

Now we define the spin velocity, $\mathcal{V}^{\mathrm{ab}}$ as the speed at
which the spin polarized in the $\mathrm{b}$   direction moves along the
$\mathrm{a}$ direction when a normal incident beam reaches the $xy$ plane with a
polarization angle $\alpha$. Then,
\begin{widetext}
\begin{align}
\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)
&= \frac{2}{\hbar}
\frac{\mu^{\mathrm{abxx}}(\omega)
E^{2}(\omega)\cos^{2}(\alpha) + 
\mu^{\mathrm{abyy}}(\omega)
E^{2}(\omega)\sin^{2}(\alpha) + 
2\mu^{\mathrm{abxy}}(\omega)
E^{2}(\omega)\cos(\alpha)\sin(\alpha)}
{\xi^{\mathrm{xx}}(\omega)
E^{2}(\omega)\cos^{2}(\alpha) + 
\xi^{\mathrm{yy}}(\omega)
E^{2}(\omega)\sin^{2}(\alpha)},
\nonumber \\
&= \frac{2}{\hbar}
\frac{\mu^{\mathrm{abxx}}(\omega)\cos^{2}(\alpha) + 
\mu^{\mathrm{abyy}}(\omega)\sin^{2}(\alpha) + 
\mu^{\mathrm{abxy}}(\omega)\sin(2\alpha)}
{\xi^{\mathrm{xx}}(\omega)\cos^{2}(\alpha) + 
\xi^{\mathrm{yy}}(\omega)\sin^{2}(\alpha)}.
\label{eq:vab}
\end{align}
\end{widetext}

For an angle $\alpha = \frac{\pi}{4}$ this expression can be reduced to 
\begin{align}
\mathcal{V}^{\mathrm{ab}} (\omega)
&= \frac{2}{\hbar}
\frac{\mu^{\mathrm{abxx}}(\omega) + \mu^{\mathrm{abyy}}(\omega) + 
2\mu^{\mathrm{abxy}}(\omega)}
{\xi^{\mathrm{xx}}(\omega) + \xi^{\mathrm{yy}}(\omega)}.
\label{eq:vab-90deg}
\end{align}

@@

\subsection{Fixing spin}\label{sec:theory-fixspin}
Considering that we have 2D structures, one of the options is fix the spin along
the $x$, $y$, or $z$ Cartesian coordinates. We define the magnitude of the spin
velocity with spin polarization along the $\mathrm{b}$ direction as 
\begin{align}
|\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)| 
&=
\sqrt{
[\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)]^{2}\ +
[\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)]^{2}\ 
}, 
\label{eq:vs-mag}
\end{align}
and the angle at which the spin velocity is directed as
\begin{align}
\gamma_{\mathrm{b}} (\omega,\alpha)
&=
\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)}
{\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)} \right),
\label{eq:gamma-ang}
\end{align}
where the angle is measured in the counter-clockwise direction from the positive
$x$ Cartesian coordinate.

@@

In a similar way we can fix the velocity on the $xy$ plane along $x$ or $y$
Cartesian coordinate and then define the magnitude of the spin velocity directed
along the $\mathrm{a}$ direction as
\begin{align}
|\mathcal{V}^{\mathrm{a}}&(\omega,\alpha)| = \nonumber \\
&\sqrt { 
[\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)]^{2} +
[\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)]^{2} +
[\mathcal{V}^{\mathrm{az}}(\omega,\alpha)]^{2} .
},
\label{eq:vv-mag}
\end{align}
Then, the spin direction depends of the components of the previous equation and
so we define the spin polar and azimuthal angles as
\begin{align}
\theta_{\mathrm{a}}  (\omega,\alpha)
=& 
\cos^{-1} \left( \frac{\mathcal{V}^{\mathrm{az}}(\omega,\alpha)}
{|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|} \right),
& 0 \leq &\theta \leq \pi, 
\label{eq:polar-ang}
\\
\varphi_{\mathrm{a}} (\omega,\alpha)
=& 
\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)}
{\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)} \right),
& 0 \leq &\varphi \leq 2\pi.
\label{eq:azimuthal-ang} 
\end{align}
where $\theta_{\mathrm{a}}(\omega,\alpha)$ is measured from the positive to the
negative $z$ Cartesian coordinate and $\varphi_{\mathrm{a}}(\omega,\alpha)$ is
measured on the $xy$ plane in the counter-clockwise direction from the positive
$x$ Cartesian coordinate.

@@

Using the Eq. \eqref{eq:vab}, we calculated the
$\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ response for the \emph{alt} and
\emph{up} 2D structures and for the CdSe and GaAs bulk systems and the results
are presented in Fig. \ref{fig:vab-str-comp}. The angle $\alpha$ presented in
the response of each structure is that for which the response is maximized in
each case.
% 
From the figure we have that the onset of the response starts when the energy of
the incoming beam is the same of the gap energy.
% 
The most intense response corresponds to the \emph{up} structure centered at
0.088\,eV corresponding to the Far Infrared (FIR) radiation and reaching a spin
velocity of 87.2\,Km/s.
% 
In the other hand, for an energy range from 0.66\,eV to 3.0\,eV, corresponding
to energies of the Near Infrared (NIR) and visible radiation, all the four
structures have contributions in the same order of magnitude.
% 
Starting with the 2D structures we have that the \emph{up} structure has other
two peaks centered at 1.94\,eV and 1.97\,eV reaching spin velocities of
22.2\,Km/s and -29.7\,Km/s, respectively, and the \emph{alt} structure has two
peaks centered at 0.72\,eV and 0.91\,eV reaching spin velocities of -40.2\,Km/s
and -32.9\,Km/s, respectively.
% 
Then, for the bulk structures we have that the CdSe has only one intense
response centered at 0.91\,eV reaching a spin velocity of -26.9\,Km/s, and the
GaAs structure has a large and almost planar zone where the response is held
reaching the maximum for an incoming beam of energy of 2.31\,eV and resulting in
a spin velocity of -21.6\,Km/s.
% 
In table \ref{tab:vab-str-comp} we present the comparison of this values for the
2D and bulk structures. We found that the most intense response for the spin
velocity of the \emph{up} structure is 3.25 times more intense than CdSe and
4.03 times more intense than the GaAs bulk structures. Also, the \emph{alt}
structure has a response more intense than the bulk systems but being less
intense than the corresponding to the \emph{up} one.
%

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-3d-svaz-1}
    \label{fig:up-3d-vsz-1}
    \\
    \includegraphics[width=\linewidth]{upplots/up-3d-svaz-2}
    \label{fig:up-3d-vsz-2}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-vaz-rag-1}
     \label{fig:up-vaz-rag-1}
    \\
    \includegraphics[width=\linewidth]{upplots/up-vaz-rag-2}
     \label{fig:up-vaz-rag-2}

@@

We first analyzed two energy ranges for the \emph{up} structure, the first for
an incoming energy beam from 0.0\,eV to 0.2\,eV which inlude the THz and the Mid
Infrared (MIR) range, where the absolute maximum of the

@@

evaluate Eq. \eqref{eq:vs-mag} using different polarization angles $\alpha$ in
Eq. \eqref{eq:vab}.

@@

In the top frames of Figs.\ref{fig:up-vaz-rag-1} and \ref{fig:up-vaz-rag-2} we

@@

same figures and frames we present in dashed lines, related to the right scale,

@@

from the evaluation of Eq. \eqref{eq:gamma-ang}, and in the bottom frames of
those figures the corresponding components

@@

parallel and perpendicular and the arrows are directed to the value of the
response corresponding to those angles.

@@

From Figs. \ref{fig:up-3d-vsz-1} and \ref{fig:up-vaz-rag-1} we have that the
absolute maximum response for the \emph{up} structure is obtained for an
incoming beam with energy of 0.088\,eV and polarization angle

@@

In the same figure the green circled box indicates the value for which the
polarization angle $\alpha$ and the response direction angle
$\gamma_{\mathrm{z}}(\omega,\alpha)$ are collinear being both angle
$65.5^{\circ}$ and resulting in a value of the response of
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=82.3$\,Km/s indicated by the
upward green arrow.

@@

$\gamma_{\mathrm{x}}(\omega,\alpha)=65.5^{\circ}$; for this angles the response
has a value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=24.8$\,Km/s
indicated by the blue downward arrow.

@@

The green and blue error bars are fixed for a value of $\pm0.5^{\circ}$ and
then, for variations of this magnitude in $\gamma_{\mathrm{z}}(\omega,\alpha)$
the complete range of $\alpha$ angle is included because this last is almost
constant.

@@

Now from Figs. \ref{fig:up-3d-vsz-2} and \ref{fig:up-vaz-rag-2} we have that a
local maxima of the response is obtained for an incoming beam with energy of
0.912\,eV and same polarization angle $\alpha=40^{\circ}$ resulting in a value
of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=30.3$\,Km/s. This comes
from a major contribution of the $\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$
component being directed in a velocity angle
$\gamma_{\mathrm{z}}(\omega,\alpha)=78^{\circ}$ on the first Cartesian Quadrant
of the $xy$ plane, for the spin polarized in the $z$ direction.

@@

Again the green circled box indicates the value for which the polarization angle
$\alpha$ and the response direction angle $\gamma_{\mathrm{z}}(\omega,\alpha)$
are collinear being both $78.5^{\circ}$ and having a response value of
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=23.5$\,Km/s indicated with
the green upward arrow. We found that for variations in the response angle of
$\pm 2^{\circ}$, indicated with the error bars, corresponds a range in the
polarization angle of $0^{\circ} \leq \alpha \leq 122^{\circ}$ having then a
large range for which the direction of the response is directed to this angle.

@@

The blue square box indicates the value for which the polarization angle and the
response angle are perpendicular being $\alpha=168.5^{\circ}$
$\gamma_{\mathrm{z}}(\omega,\alpha)=78.5^{\circ}$ and having a response
the blue upward arrow. Again, for variations in the response angle of
$\pm2^{\circ}$, indicated with the error bars, corresponds a range in the
polarization angle of $155^{\circ} \leq \alpha \leq 180^{\circ}$ having again a
large range for which the direction of the response is held.
The most interesting case in which the spin is perpendicular to the surface of
the structure and also for the \emph{up} structure the most intense was the
presented before for which the spin is polarized in the $\mathrm{z}$ direction.

@@

in the $\mathrm{x}$ and $\mathrm{y}$ direction but we do not present the
corresponding plots. For those cases we have that the absolute maxima response
is obtained for an energy of the incoming beam equal to 0.088\,eV and
polarization angle $\alpha=40^{\circ}$ resulting in values of

@@

\textbf{Up structure.}
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-3d-vxb-1}
    \label{fig:up-3d-vvx-1}
    \\
    \includegraphics[width=\linewidth]{upplots/up-3d-vyb-1}
    \label{fig:up-3d-vvy-1}

    \caption{ $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$responses as a function of the
    photon energy and polarization angle $\alpha$ for the \emph{up} structure.
    The absolute maxima of both are localized in the energy range from 0.08\,eV
    to 0.10\,eV, in the Far  Infrared, and for polarization angles from
    $25^{\circ}$ to $50^{\circ}$.}
    \label{fig:up-3d-vva-1}
\end{figure}
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m1}
    \label{fig:up-vx-comp-rtp-1}
    \\
    \includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m1}
    \label{fig:up-vy-comp-rtp-1}

@@

% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV
% %% Description of UP |V^{a}| 3D
% %%%%%%%%%%%%%%%%%
For the \emph{up} structure we first analyzed the energy range from 0.00\,eV to
0.16\,eV, where we found the most intense response and the absolute maxima for
$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ presented in Fig.
% 
\ref{fig:up-3d-vva-1} and resulting from evaluate Eq. \eqref{eq:vv-mag} as a
function of the polarization angle $\alpha$ in Eq. \eqref{eq:vab} for the
\emph{up} structure.
%
From this picture we can see that for the zone between the energy range of
0.084\,eV-0.093\,eV and polarization angles between $30^{\circ}$ and
$45^{\circ}$ is the zone where the maximum response is held for both,
$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$.
% %%%%%%%%%%%%%%%%%
% %% 1.8 eV - 2.0 eV
% %% Description of UP |V^{a}|, components and RTP
% %%%%%%%%%%%%%%%%%

>>>>

\section{Introduction}
\blindtext
\begin{figure}[ht!]
    \centering
    \includegraphics[width=\linewidth]{figures/altstruc2}
    \\
    \includegraphics[width=\linewidth]{figures/altstruc1}
    \caption{Alt structure.}
    \label{fig:alt-struc}
\end{figure}
\begin{figure}[ht!]
    \centering
    \includegraphics[width=\linewidth]{figures/upstruc2}
    \\
    \includegraphics[width=\linewidth]{figures/upstruc1}
    \caption{Up structure}
    \label{fig:up-struc}
\end{figure}
\blindtext
\blindtext

@@

The spin density injection current $\dot{K}^{\mathrm{ab}}$ can be written in
terms of a material response pseudotensor $\mu^{\mathrm{abcd}}(\omega)$ as
% with speed along direction $\mathrm{a}$ and spin
% polarization along $\mathrm{b}$ is defined as
\begin{equation*}
\dot{K}^{\mathrm{ab}}(\omega) = \mu^{\mathrm{abcd}}(\omega)
E^{\mathrm{c}}(\omega) E^{\mathrm{d*}}(\omega)
\label{eq:dotk}
\end{equation*}
where the roman superscripts denote Cartesian components corresponding
$\mathrm{a}$ to the spin velocity direction and $\mathrm{b}$ to the spin
polarization direction and the pseudotensor can be written as
\begin{widetext}
\begin{align}
\mu^{\mathrm{abcd}} (\omega) 
&=
\frac{\pi e^{2}}{\hbar^{2}} \int 
\frac{d^{3}K}{8 \pi^{3}}
\sum_{vcc'}^{'}
\mathrm{Re} \left[ K^{\mathrm{ab}}_{cc'} 
\left( 
r^{\mathrm{c}}_{vc'} 
r^{\mathrm{d}}_{cv } +
(c \leftrightarrow d)
\right) 
\right]
\delta(\omega-\omega_{cv})
\label{eq:mu}
% \\
% K^{\mathrm{ab}}_{mn}
% &=
% \sum_{\ell}v^{\mathrm{a}}_{nl} S^{\mathrm{b}}_{lm}
% \label{eq:velspi-matelem}
\end{align}
\end{widetext}
where $K^{\mathrm{ab}}_{mn}(\mathbf{k}) =
\sum_{\ell}v^{\mathrm{a}}_{nl}(\mathbf{k}) S^{\mathrm{b}}_{lm}(\mathbf{k})$ are
the spin current matrix elements that, using time reversal invariance,
$K^{\mathrm{ab}}_{nm}(\mathbf{-k}) = K^{\mathrm{ab*}}(\mathbf{k}) $. The $'$ in
the sum means that $c$ and $c'$ are quasi degenerate states and the sum only
covers these states and since $mu$ is real we have that
$\mu^{\mathrm{abcd}}(\omega) = \mu^{\mathrm{abdc}}(\omega)$.

Now we define the spin velocity, $\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ as
the speed at which the spin polarized in the $\mathrm{b}$   direction moves
along the $\mathrm{a}$ direction when a normal incident beam reaches the $xy$
plane with a polarization angle $\alpha$. Then,
\begin{widetext}
\begin{align}
\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)
&= \frac{2}{\hbar}
\frac{\mu^{\mathrm{abxx}}(\omega)
E^{2}(\omega)\cos^{2}(\alpha) + 
\mu^{\mathrm{abyy}}(\omega)
E^{2}(\omega)\sin^{2}(\alpha) + 
2\mu^{\mathrm{abxy}}(\omega)
E^{2}(\omega)\cos(\alpha)\sin(\alpha)}
{\xi^{\mathrm{xx}}(\omega)
E^{2}(\omega)\cos^{2}(\alpha) + 
\xi^{\mathrm{yy}}(\omega)
E^{2}(\omega)\sin^{2}(\alpha)},
\nonumber \\
&= \frac{2}{\hbar}
\frac{\mu^{\mathrm{abxx}}(\omega)\cos^{2}(\alpha) + 
\mu^{\mathrm{abyy}}(\omega)\sin^{2}(\alpha) + 
\mu^{\mathrm{abxy}}(\omega)\sin(2\alpha)}
{\xi^{\mathrm{xx}}(\omega)\cos^{2}(\alpha) + 
\xi^{\mathrm{yy}}(\omega)\sin^{2}(\alpha)},
\label{eq:vab}
\end{align}
\end{widetext}
where $\xi^{\mathrm{aa}}(\omega)$ are the carrier generation rate tensor
components\cite{arzatePRB14}.
% 
For an angle $\alpha = \frac{\pi}{4}$ this expression can be reduced to 
\begin{align}
\mathcal{V}^{\mathrm{ab}} (\omega)
&= \frac{2}{\hbar}
\frac{\mu^{\mathrm{abxx}}(\omega) + \mu^{\mathrm{abyy}}(\omega) + 
2\mu^{\mathrm{abxy}}(\omega)}
{\xi^{\mathrm{xx}}(\omega) + \xi^{\mathrm{yy}}(\omega)}.
\label{eq:vab-90deg}
\end{align}

@@

\subsection{Fixing spin}\label{sec:theory-fixspin}
Considering that we have 2D structures, one of the options is fix the spin along
the $x$, $y$, or $z$ Cartesian coordinates. We define the magnitude of the spin
velocity with spin polarization along the $\mathrm{b}$ direction as 
\begin{align}
|\mathcal{V}_{\sigma^{\mathrm{b}}}(\omega,\alpha)| 
&=
\sqrt{
[\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)]^{2}\ +
[\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)]^{2}\ 
}, 
\label{eq:vs-mag}
\end{align}
and the angle at which the spin velocity is directed on the $xy$ plane as
\begin{align}
\gamma_{\mathrm{b}} (\omega,\alpha)
&=
\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)}
{\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)} \right),
\label{eq:gamma-ang}
\end{align}
where the angle is measured in the counter-clockwise direction from the positive
$x$ Cartesian coordinate. We also define two special angles
\begin{align}
\gamma_{\mathrm{b \parallel}}(\omega,\alpha) &= \alpha, 
\label{eq:gammapar} 
\\
\gamma_{\mathrm{b \perp}}(\omega,\alpha) &= \alpha \pm 90^{\circ}.
\label{eq:gammaperp}
\end{align}
The first corresponds to the case when the spin velocity is directed, on the
$xy$ plane in the same direction of the polarization angle of the incoming beam;
the second one corresponds to the case when the spin velocity is directed
perpendicularly respect to the polarization angle of the incoming beam.

@@

In a similar way we can fix the velocity on the $xy$ plane along $x$ or $y$
Cartesian coordinate and then define the magnitude of the spin velocity directed
along the $\mathrm{a}$ direction as
\begin{align}
|\mathcal{V}^{\mathrm{a}}&(\omega,\alpha)| = \nonumber \\
&\sqrt { 
[\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)]^{2} +
[\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)]^{2} +
[\mathcal{V}^{\mathrm{az}}(\omega,\alpha)]^{2} .
},
\label{eq:vv-mag}
\end{align}
Then, the spin direction depends of the components of the previous equation and
so we define the spin orientation polar and azimuthal angles as
\begin{align}
\theta_{\mathrm{a}}  (\omega,\alpha)
=& 
\cos^{-1} \left( \frac{\mathcal{V}^{\mathrm{az}}(\omega,\alpha)}
{|\mathcal{V}^{\mathrm{a}}(\omega,\alpha)|} \right),
& 0 \leq &\theta \leq \pi, 
\label{eq:polar-ang}
\\
\varphi_{\mathrm{a}} (\omega,\alpha)
=& 
\tan^{-1} \left( \frac{\mathcal{V}^{\mathrm{ay}}(\omega,\alpha)}
{\mathcal{V}^{\mathrm{ax}}(\omega,\alpha)} \right),
& 0 \leq &\varphi \leq 2\pi.
\label{eq:azimuthal-ang} 
\end{align}
where $\theta_{\mathrm{a}}(\omega,\alpha)$ is measured from the positive to the
negative $z$ Cartesian coordinate and $\varphi_{\mathrm{a}}(\omega,\alpha)$ is
measured on the $xy$ plane in the counter-clockwise direction from the positive
$x$ Cartesian coordinate.

@@

Using the Eq. \eqref{eq:vab}, we calculated the
$\mathcal{V}^{\mathrm{ab}}(\omega,\alpha)$ response for the \emph{alt} and
\emph{up} 2D structures and for the CdSe and GaAs bulk systems and the results
are presented in Fig. \ref{fig:vab-str-comp}. The angle $\alpha$ presented in
the response of each structure is that for which the response is maximized in
each case.
% 
From the figure we have that the onset of the response starts when the energy of
the incoming beam is the same of the gap energy.
% 
The most intense response corresponds to the \emph{up} structure centered at
0.088\,eV corresponding to the Far Infrared (FIR) radiation and reaching a spin
velocity of 87.2\,Km/s.
% 
In the other hand, for an energy range from 0.66\,eV to 3.0\,eV, corresponding
to energies of the Near Infrared (NIR) and visible radiation, all the four
structures have contributions in the same order of magnitude.
% 
Starting with the 2D structures we have that the \emph{up} structure has other
two peaks centered at 1.94\,eV and 1.97\,eV reaching spin velocities of
22.2\,Km/s and -29.7\,Km/s, respectively, and the \emph{alt} structure has two
peaks centered at 0.72\,eV and 0.91\,eV reaching spin velocities of -40.2\,Km/s
and -32.9\,Km/s, respectively.
% 
Then, for the bulk structures we have that the CdSe has only one intense
response centered at 0.91\,eV reaching a spin velocity of -26.9\,Km/s, and the
GaAs structure has a large and almost planar zone where the response is held
reaching the maximum for an incoming beam of energy of 2.31\,eV and resulting in
a spin velocity of -21.6\,Km/s.
% 
A negative quantity in the spin velocity means a change in the spin polarization traveling in the opposite direction.
% 
In table \ref{tab:vab-str-comp} we present the comparison of this values for the
2D and bulk structures. We found that the most intense response for the spin
velocity of the \emph{up} structure is 3.25 times more intense than CdSe and
4.03 times more intense than the GaAs bulk structures. Also, the \emph{alt}
structure has a response more intense than the bulk systems but being less
intense than the corresponding to the \emph{up} one.
%

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-3d-svaz-1}
    \\
    \includegraphics[width=\linewidth]{upplots/up-3d-svaz-2}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-vaz-rag-1}
    \\
    \includegraphics[width=\linewidth]{upplots/up-vaz-rag-2}

@@

The most interesting case is that for which the spin is perpendicular to the
surface corresponding to $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$.
For this case we first analyzed two energy ranges for the \emph{up} structure,
the first for an incoming energy beam from 0.0\,eV to 0.2\,eV which include the
THz and the Mid Infrared (MIR) range, where the absolute maximum of the

@@

evaluate Eq. \eqref{eq:vs-mag}.

@@

In the top frames of top and bottom panels of Fig. \ref{fig:up-vaz-rag} we

@@

same panels and frames we present in dashed lines, related to the right scale,

@@

from evaluate Eq. \eqref{eq:gamma-ang}, and in the bottom frames the
panels we present the corresponding components

@@

parallel (Eq. \ref{eq:gammapar}) and perpendicular (Eq. \ref{eq:gammaperp}) and
the arrows are directed to the value of the response corresponding to those
angles.

@@

From top panels of Figs. \ref{fig:up-3d-vsz} and \ref{fig:up-vaz-rag} we have
that the absolute maximum response for the \emph{up} structure is obtained for
an incoming beam with energy of 0.088\,eV and polarization angle

@@

From the top panel of Fig. \ref{fig:up-vaz-rag} we have that the velocity angle
is almost constant for all the polarization angle range having values of
$\gamma_{\mathrm{z}}(\omega,\alpha) = 65.5^{\circ} \pm 0.5^{\circ}$. In this
panel the green circled box indicates the value for which the polarization angle
and the response direction angle are collinear (Eq. \ref{eq:gammapar}) being
$\gamma_{\mathrm{z}\parallel}(\omega,\alpha) = 65.5^{\circ}$ and resulting in a
value of the response of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| =
82.3$\,Km/s indicated by the upward green arrow.

@@

$\gamma_{\mathrm{z}\perp}(\omega,\alpha)=65.5^{\circ}$; for this angle the
response has a value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| =
24.8$\,Km/s indicated by the blue downward arrow.

@@

Now, from bottom panels of Figs. \ref{fig:up-3d-vsz} and \ref{fig:up-vaz-rag} we
have that a local maximum of the response is obtained for an incoming beam with
energy of 0.912\,eV and same polarization angle $\alpha=40^{\circ}$ resulting in
a value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=30.3$\,Km/s. This
comes from a major contribution of the
$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$ component being directed in a
velocity angle $\gamma_{\mathrm{z}}(\omega,\alpha)=78^{\circ}$ on the first
Cartesian Quadrant on the $xy$ plane, for the spin polarized in the $z$
direction.

@@

Again from the bottom panel of Fig. \ref{fig:up-vaz-rag} we found that the
velocity angle is almost constant at $78^{\circ}$ and has variations of
$1^{\circ}$ for polarization angles between $0^{\circ}$ and $100^{\circ}$. In
this range the green circled box indicates the value for which the polarization
angle and the response direction angle are collinear corresponding to
$\gamma_{\mathrm{z}\parallel}(\omega,\alpha) = 78.5^{\circ}$ and having a
response value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| =
23.5$\,Km/s indicated with the green upward arrow.

@@

Finally, the blue square box indicates the value for which the polarization
angle and the response angle are perpendicular being $\alpha=168.5^{\circ}$
$\gamma_{\mathrm{z}\perp}(\omega,\alpha) = 78.5^{\circ}$ and having a response
the blue upward arrow.

@@

@@

along the $\mathrm{x}$ and $\mathrm{y}$ Cartesian coordinates but we do not
present here the corresponding plots. For those cases we have that the absolute
maxima responses are obtained for an energy of the incoming beam equal to
0.088\,eV and polarization angle $\alpha=40^{\circ}$ resulting in values of

@@

\textbf{Up structure.}
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-3d-vxb-1}
    \\
    \includegraphics[width=\linewidth]{upplots/up-3d-vyb-1}

    \caption{ $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
    $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$responses as a function of the
    photon energy and polarization angle $\alpha$ for the \emph{up} structure.
    The absolute maxima of both are localized in the energy range from 0.08\,eV
    to 0.10\,eV, in the Far  Infrared, and for polarization angles from
    $25^{\circ}$ to $50^{\circ}$.}
    \label{fig:up-3d-vva-1}
\end{figure}
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m1}
    \\
    \includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m1}

@@

% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV
% %% Description of UP |V^{a}| 3D
% %%%%%%%%%%%%%%%%%
In top and bottom panels of Fig. \ref{fig:up-3d-vva-1} we present
$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ resulting from evaluate the Eq.
\eqref{eq:vv-mag} in the energy range from 0.00\,eV to 0.16\,eV for the
\emph{up} structure.
%
From this figure we can see that for the zone between the energy range of
0.084\,eV-0.093\,eV and polarization angles between $30^{\circ}$ and
$45^{\circ}$ is the zone where the maximum response is held for both,
$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$.
% %%%%%%%%%%%%%%%%%
% %% 1.8 eV - 2.0 eV
% %% Description of UP |V^{a}|, components and RTP
% %%%%%%%%%%%%%%%%%

In the top frames of top and bottom panel of Fig. \ref{fig:up-vab-comp-rtp-1} we
present in solid lines the results of
$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ and
$|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$, related to the left scale, fixing
the polarization angle to $\alpha=40^{\circ}$ for which the response is
maximized. In the same panels and frames we present in dashed lines the
corresponding polar $\theta_{a}(\omega,\alpha)$ and azimuthal
$\varphi_{a}(\omega,\alpha)$ spin angles related to the right scale. Also, in
the bottom frames we present the corresponding components
$\mathcal{V}^{\mathrm{xx}}(\omega,\alpha)$,
$\mathcal{V}^{\mathrm{xy}}(\omega,\alpha)$,
$\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$, and
$\mathcal{V}^{\mathrm{yx}}(\omega,\alpha)$,
$\mathcal{V}^{\mathrm{yy}}(\omega,\alpha)$,
$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$.
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{upplots/up-3d-vxb-2}
    \label{fig:up-3d-vvx-2}
    \\
    \includegraphics[width=\linewidth]{upplots/up-3d-vyb-2}
    \label{fig:up-3d-vvy-2}
